Boolean Operations for Surfaces in VTK Without External Libraries

### 2011-05-10 Document/LaTeX/Article.tex
Added docs on vtkImplicitPolyData.

@@

\input{ResultsFigure.tex}

>>>>

The class \code{vtkImplicitPolyData} has several options that can be set. Use
\begin{verbatim}
void SetNoValue(double value);
\end{verbatim}
to set the value returned by \code{double EvaluateFunction(double x[3])} when an error occurs. Likewise,
\begin{verbatim}
void SetNoGradient(double value[3]);
\end{verbatim}
to set the gradient returned when an error is encountered. Finally,
\begin{verbatim}
void SetTolerance(double tolerance);
\end{verbatim}
is used to determine when the absolute value of the signed distance is close enough to zero to be considered zero.

@@

%\input{ResultsFigure.tex}
